A pipeline to analyse time-course gene expression data

### 2019-10-08 scripts/manuscript.Rmd
FIX create_moanin_model now returns an object
ENH DE_timecourse now provides q-values in addition of p-values

**EAP**: this makes it sound like you create a class, but in fact it's just a list. Wouldn't it be helpful to make it a class?

@@

# The function takes the data (data.frame or named matrix), the meta data
# (data.frame containing a timepoint and group column, the first corresponding
# to the time-course information, the latter corresponding to the
# treatment).
pvalues = DE_timecourse(
    data, moanin_model, timecourse_contrasts,
    use_voom_weights=FALSE)
qvalues = apply(pvalues, 2, p.adjust)

**EAP: is there a reason that the qvalues aren't provided with the output like in `DE_timepoints`? Doesn't that risk the user not taking that step and working with the unadjusted p-values?**

@@

```{r fig.height=4, fig.width=4}
pvalue = qvalues[, "M-K"]
lfc_timecourse = log_fold_change_timecourse[, "M-K"]
names(lfc_timecourse) = row.names(log_fold_change_timecourse)

@@

```{r filter_genes}
# Then rank by fisher's p-value and take max the number of genes of interest
# Filter out q-values for the pvalues table
fishers_pval = pvalues_fisher_method(pvalues)
fishers_qval = p.adjust(fishers_pval)

@@

**EAP: `subsample_proportion` was set to 1 in the code, but shouldn't it be
0.8? I changed it to 0.8. But it seems like you don't actually run this code,
but read existing runs, so maybe was right there?**

**Nelle: that was a mistake in the code. I don't actually run subsampling
experiments: only the bootstrap, and it's done in a separate file as it is too
time consuming to run in an Rmd file**

>>>>

@@

# The function takes the data (data.frame or named matrix), the meta data
# (data.frame containing a timepoint and group column, the first corresponding
# to the time-course information, the latter corresponding to the
# treatment).
DE_results = DE_timecourse(
    data, moanin_model, timecourse_contrasts,
    use_voom_weights=FALSE)
pval_columns = colnames(DE_results)[
    grepl("pval", colnames(DE_results))]
qval_columns = colnames(DE_results)[
    grepl("qval", colnames(DE_results))]
pvalues = DE_results[, pval_columns]
qvalues = DE_results[, qval_columns]
```

@@

```{r fig.height=4, fig.width=4}
pvalue = DE_results[, "M-K_pval"]
names(pvalue) = row.names(DE_results)
lfc_timecourse = log_fold_change_timecourse[, "M-K"]
names(lfc_timecourse) = row.names(log_fold_change_timecourse)

@@

```{r filter_genes}
# Then rank by fisher's p-value and take max the number of genes of interest
# Filter out q-values for the pvalues table
fishers_pval = pvalues_fisher_method(pvalues)
qvalues = apply(pvalues, 2, p.adjust)
fishers_qval = p.adjust(fishers_pval)

@@
